---
title: "Bootstrapping"
author: "Lory Salazar"
date: "3/4/2021"
output: 
  html_document: 
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(boot)
```

```{r}
# First creating a row for those who responded whether they experienced exclusionary, offensive, hostile, or intimidating conduct
conduct <- rep(c(0,1), times = c(14,22))

# Then turning it into a data frame 
df <- data.frame(conduct)
```

```{r}
# Creating a function to calculate the proportions of each bootstrapped sample
prop_fun <- function(x,i) {sum(x[i]==1)/length(x)}

# Creating 10,000 bootstrap samples by resampling from the conduct vector, using the function to calculate the mean of each:
boot_10k <- boot(conduct, 
                 statistic = prop_fun, 
                 R = 10000)

boot_10k_df <- data.frame(bs_prop = boot_10k$t)

ggplot(data = boot_10k_df, aes(x = bs_prop)) +
  geom_histogram() +
  theme_minimal() +
  labs(title = "Proportion of nonbinary/genderqueer students experiencing exclusionary, hostile,\nor intimidating experience at UCSB",
       x = "Proportion of nonbinary/genderqueer students",
       y = "Counts")


```

**Figure 1.** Counts of proportions of nonbinary/genderqueer students at UCSB who responded "yes" in a survey asking if they had personally experienced “exclusionary, offensive, hostile or intimidating conduct”.

```{r}
boot.ci(boot_10k, conf = 0.95, type = "perc")
```


We used bootstrapping to create resamples with replacement to find a sampling distribution that is based on more than one sample. From the created distribution, we found a 95% confidence interval of (0.4, 0.8). This means that we are 95% confident that the true proportion of nonbinary/genderqueer individuals who experienced misconduct at UCSB is contained within (0.4, 0.8).


