---
title: "Parameter Estimation"
author: "Lory Salazar"
date: "3/3/2021"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(here)
library(boot)
library(gt)
library(patchwork)
library(broom)
library(nlstools)
library(janitor)
```

```{r}
# Read in the data and add a column to assign numerical values to the years
fish_catch <- read.csv(here("data","fish_catch.csv"), skip = 2) %>% 
  drop_na() %>% 
  clean_names() %>% 
  mutate(year_number = 0:62) 

# Changing from character to numeric class
fish_catch$wild_catch <- as.numeric(fish_catch$wild_catch)
fish_catch$year <- as.numeric(fish_catch$year)

```

```{r}
# Creating an exploratory plot to look at fish catches over time
ggplot(data = fish_catch, aes(x = year_number, y = wild_catch)) +
  geom_point() +
  theme_minimal() +
  scale_y_continuous(breaks = c(10,20,30,40,50,60,70,80,90,100))

# Finding initial estimates 
fish_exp <- fish_catch %>% 
  mutate(ln_wild = log(wild_catch))

lm_k <- lm(ln_wild ~ year_number, data = fish_exp)

# Constant level reached at around 90 = K, catch at year 0 is around 17 so A ~ (90-17)/17 ~ 4.5
```

**Figure 1.** In text below the exploratory graph: What type of relationship describes the trend? What does that look like mathematically (include an equation, possibly using LaTeX)? What are your initial estimates for the parameters in the model? 

The relationship between wild catches and time is described by logistic growth, which is described mathematically as:

$P(t)=\frac{K}{1+Ae^{-kt}}$

Where:

- $K$ is the carrying capacity
- $A$ is $\frac{K-P_0}{P_0}$
- $k$ is the growth rate constant

Our initial estimates are: *k* is around 0.03, *K* is around 90, and *A* is around 4.5. 

## non-linear least sq



