---
title: "Agglomerative hierarchical clustering"
author: "Lory Salazar"
date: "3/2/2021"
output: 
  html_document: 
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(here)
library(NbClust)
library(cluster)
library(factoextra)
library(dendextend)
library(ggdendro)
```

## Hierarchial clustering of water chemistry in Santa Barbara
In this report, we perform hierarchical clustering by complete linkage, then create a dendrogram showing multivariate clustering for water stream chemistry by site in the Santa Barbara coastal drainage area.

```{r}
# Read in the data
water_chem <- read_csv(here("data", "sbc_lter_registered_stream_chemistry.csv")) %>% 
  select(site_code, nh4_uM:spec_cond_uSpercm) %>% 
  na_if(-999)

# Getting the average by site
water_summary <- water_chem %>% 
  rowwise() %>% 
  mutate(summary = mean(
    c_across(nh4_uM:spec_cond_uSpercm), na.rm = TRUE)
    ) %>% 
  select(site_code, summary) %>% 
  group_by(site_code) %>% 
  summarise(mean = mean(summary))
```

```{r, fig.show='hide'}
# Scale the numeric variables (column 2, which is the mean/summary we calculated)
water_scaled <- water_summary %>% 
  select(2) %>% 
  scale()
  

# Update to add rownames (site code) from our previous data set
rownames(water_scaled) <- water_summary$site_code

# Find the Euclidean distances
euc_distance <- dist(water_scaled, method = "euclidean")

# Hierarchical clustering (complete linkage)
hc_complete <- hclust(euc_distance, method = "complete" )

# Creating a basic plot (base plot):
plot(hc_complete, cex = 0.6, hang = -1)
```

```{r}
# Plotting using ggdendogram
ggdendrogram(hc_complete, 
             rotate = TRUE) +
  theme_minimal() +
  labs(x = "Site code",
       title = "Multivariate clustering for stream chemistry in Santa Barbara coastal drainage") +
  ylim(0,0.7)
```

**Figure 1.** A dendrogram describing the hierarchical clustering of the stream chemistry in Santa Barbara coastal drainage, based on site and using complete linkages. Clusters are merged by the *smallest maximum* distance between two observations in distinct clusters.

## Data citation
Santa Barbara Coastal LTER and J. Melack. 2019. SBC LTER: Land: Stream chemistry in the Santa Barbara Coastal drainage area, ongoing since 2000 ver 16. Environmental Data Initiative. https://doi.org/10.6073/pasta/67a558a24ceed9a0a5bf5e46ab841174 (Accessed 2021-03-02).
